\documentclass[12pt]{article}
\usepackage{setspace, graphicx, fullpage, amssymb, amsmath, epsfig, natbib, array, multirow, hyperref}
\usepackage{amsfonts, bm} 
\usepackage{dcolumn}
\usepackage{subfigure, float} 
\usepackage[margin=0.75in]{geometry} 
\usepackage{verbatim}
\usepackage{url}
\usepackage{enumerate}
\newcolumntype{d}[1]{D{.}{.}{#1}} 

\begin{document}

\begin{center}
\Large Draft Codebook
\end{center}

\begin{itemize}
	\item \verb|congress|: Congress Number of Observation
	
	\item \verb|icpsrLegis|: ICPSR Number of Legislator
	
	\item \verb|stabb|: State Abbreviation
	
	\item \verb|class|: Senator Class (for Election)
	
	\item \verb|first_name|: First Name of Legislator
	
	\item \verb|mc|: Last Name and State Abbreviation of Legislator 
	
	Senators who served discontinuous terms have information about which period of service the observation is for. For non-unique combinations of these in the Senate (such as parent-child pairings), the ICPSR Number is included after the state abbreviation.
	
	\item \verb|caucus|: The Party a Senator Caucused With
	
	\item \verb|caucus_majority|: Majority Party Status
	
	Takes 1 when the a party caucus is in the majority and a 0 when it is in the minority. Because majority party status switched during Congress 107 it is treated as a special case. For this Congress, Democrats (who were the majority for a longer period) receive 0.75, Republicans (who were the majority for a shorter period) receive 0.25, and Sen. Jeffords (who always caucused with the majority party) receives 1.
	
	\item \verb|pres_vote_share|: Most Recent Same Party Presidential Vote Percent in Senator's State
	
	Members not of one of the two major parties receive the presidential vote share of the party they caucused with in the Senate
	
	\item \verb|pres_dem_vote_share|: Most Recent Democratic Presidential Vote Percent in Senator's State
	
	\item \verb|vote_share|: Two Party Vote Share Received by Senator in Most Recent Election
	
	Members not of one of the two major parties are paired against their next closest opponent
	
	\item \verb|south|: Dummy Indicator for Serving in the 13 State South
	
	\item \verb|south11|: Dummy Indicator for Serving in the 11 State South
	
	\item \verb|south13|: Dummy Indicator for Serving in the 13 State South
	
	This should be identical to the \item \verb|south| variable.
	
	\item \verb|south17|: Dummy Indicator for Serving in the 17 State South
	
	\item \verb|south_dem|: Dummy Indicator for Democrats Serving in the South
	
	\item \verb|leader|: Dummy Indicator for Party Leadership As Listed in the Almanac of American Politics
	
	\item \verb|chair|: Dummy Indicator for Committee Chairs
	
	\item \verb|best_committee|: Best Committee Value
	
	Ranks committee assignments from worst (lower values) to best (higher values) based on ``The Value of Committee Assignments in Congress since 1994'' Edwards \& Stewart (2006). These are divided into 3 periods: Congresses 81-95, 96-102, 103-112 based on cutoffs within this paper for these values. Takes 0 if a Senator was not on a committee in the Congress.
	
	\item \verb|power_committee|: Dummy Indicator for Being on One of the Top 4 Committees
	
	\item \verb|up_for_reelection|: Dummy Indicator for Being Up for Reelection at the End of the Congress
	
	\item \verb|freshman|: Dummy Indicator for First Term in Senate
	
	This value takes 1 for the first three Congresses in which a Senator who has previously served returns to the Senate.
	
	\item \verb|superfreshman|: Dummy Indicator for First Term of a Previously Serving Senator Returning to the Senate
	
	\item \verb|seniority|: Number of Consecutive Congresses Served
	
	Indicator for the number of consecutive Congresses served by a Senator. Minimum value 1.
	
	\item \verb|senate_seniority|: Number of Senate Term Lengths Served by a Senator 
		
	Indicator for the number of consecutive sets of 3 Congresses served by a Senator. Minimum value 1.
	
	\item \verb|retiree|: Dummy Indicator for Senators Who Retired
	
	\item \verb|afam|: Dummy Indicator for African American Senators
	
	\item \verb|female|: Dummy Indicator for Female Senators
	
	\item \verb|latino|: Dummy Indicator for Hispanic and Latino Senators
	
	\item \verb|gingrich_senator|: Dummy Indicator for Theriault (2013) Gingrich Senators
\end{itemize}











\end{document}